\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/conclusion.tex
Update conclusion.tex
Acknowledgement
Update
Update conclusion.tex
user study remove from conclu

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB. The video capture mode proved practical and powerful, as it extracts
victim's sensitive information in a stealthy way. The fully control mode
achieves the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

>>>>

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB. The video capture mode proved practical and powerful, as it extracts
victim's sensitive information in a stealthy way. The fully control mode
achieves the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes. In our experiment, we
obtain and analyze video stream extracted from 11 applications with \tool,
which demonstrates its capability in a simulated real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

\section{Acknowledgement}
We are very grateful to our shepherd, Michael Schwarz and the anonymous reviewers for their valuable comments that improved the paper.
